---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hurwitzLab

<!-- badges: start -->
<!-- badges: end -->

In Hurwitz Lab, we take pride in conveying information with elegant 
figures. We also like a level of consistency in the work produced by our
group. This package provide color palettes and themes to be used when
producing figures in R.

## Installation

You can install hurwitzLab with:

``` r
devtools::install_github("schackartk/hurwitzLab")
```

## What's here?

This package currently provides color palettes for Hurwitz Lab.

### Available Color Palettes

The following palettes are available: main, classic, gray

Palettes can be previewed using the `display_hurwitz_pal()` function:

```{r previewing}
library(hurwitzLab)

display_hurwitz_pal(3, "main")
```



## Examples

Usage is similar to other palette packages. Functions are available for both 
scale_fill and scale_color.

```{r example}
library(hurwitzLab)
library(ggplot2)

ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) +
  geom_point() +
  theme_light() +
  hurwitzLab::scale_color_hurwitz()
```

Palettes can be used for continuous variables too:

```{r continuous}
library(hurwitzLab)
library(ggplot2)

ggplot(iris, aes(x = Sepal.Width, y = Sepal.Length, color = Petal.Length)) +
  geom_point() +
  theme_light() +
  scale_color_hurwitz(discrete = FALSE, palette = "classic")
```


