---
title: "hurwitzLab"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{hurwitzLab}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 5
)
```

```{r setup}
library(hurwitzLab)
```

This package provides palettes and scales based on these colors:

```{r colors, message = FALSE, warning = FALSE, echo = FALSE}
library(dplyr)
library(gt)

hurwitz_colors <- get_hurwitz_colors()

tibble(
    name = names(hurwitz_colors),
    color_hex = hurwitz_colors,
  ) %>% 
  gt() %>% 
  data_color(columns = "color_hex",
             colors = scales::col_factor(palette = hurwitz_colors,
                                         domain = hurwitz_colors,
                                         ordered = TRUE)) %>% 
  tab_header(title = "hurwitzLab colors") %>% 
  cols_label(name = "Name", color_hex = "Color")
```


# Scaling Colors or Fill in `ggplot2`

Scale functions are provided which can be added directly to a 
gplot2 object. Usage is similar to `rColorBrewer::scale_color_brewer()` or `viridis::scale_color_viridis()`.

### Scaling colors
```{r scale_colors}
library(ggplot2)

ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) +
  geom_point(size = 2) +
  theme_light() +
  scale_color_hurwitz(palette = "distinguish")
```

### Scaling fill

```{r scale_fill}
ggplot(iris, aes(x = Species, y = Sepal.Width, fill = Species)) +
  geom_boxplot() +
  theme_light() +
  scale_fill_hurwitz(palette = "shallow_ocean")
```

## Scales for Continuous Variable

A pallette can be applied to a continuous variable by setting `discrete = FALSE`:

```{r continuous}
ggplot(iris, aes(x = Sepal.Width, y = Sepal.Length, color = Petal.Length)) +
  geom_point() +
  theme_light() +
  scale_color_hurwitz(discrete = FALSE, palette = "classic")
```

Colors to use can be manually assigned using `ggplot2::scale_color_gradientn()`. To access colors we can use `get_hurwitz_colors()` which is detailed below.

```{r continuous_custom}
library(scales)

ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color = Petal.Width)) +
  geom_point() +
  theme_light() +
  scale_color_gradientn(colors = get_hurwitz_colors("red", "teal"))
```

## Reversing a palette

```{r reverse}
ggplot(iris, aes(x = Species, y = Sepal.Width, fill = Species)) +
  geom_boxplot() +
  theme_light() +
  scale_fill_hurwitz(palette = "shallow_ocean", reverse = TRUE)
```



# Accessing Colors and Palettes

### Names and Hex Codes

All colors in this package can be accessed by calling `get_hurwitz_colors()`:
```{r get_colors}
get_hurwitz_colors()
```

Alternatively, the hex code of specific colors can be accessed:
```{r get_some_colors}
get_hurwitz_colors("charcoal", "teal")
```

To see the hex codes of all colors in a specific palette:
```{r hurwitz_pal}
hurwitz_pal("distinguish2")
```


### Previewing palettes

Palettes can be previewed using the function `display_hurwitz_pal()`:

```{r display_pal}
display_hurwitz_pal("main")
```

You can also see which colors will be used when the number of categories is different from the number of colors in a pallette by specifying `n`.

```{r displauy_pal_n}
display_hurwitz_pal("main", 2)
```

